---
title: "Dirty Data Project - Group 1: Linzi, Lorna, Debbie, Gosia"
output: html_document
date: "2023-03-16"
---

# **1. Project Brief**

The task assigned to our group was to clean, tidy, and combine three datasets into one set, and answer a series of analysis questions.

The three datasets contained survey information on Halloween habits and preferences, with respondents asked to rate a series of candy items.


### **1.1. Raw Datasets - Observations**

The three datasets were observed to be non-uniform, with each dataset containing unique columns in comparison to the others as well as sharing some commonalities. This gave the group the first indications on how to begin cleansing the data before attempting to combine into one large dataset.


# **2. Data Cleaning - Methodology and Action Plan**

The datasets were read into our R script.

Our group of four decided to divide in the first instance and do a preliminary investigation of the datasets; three of us took a dataset each to scope out the variables and report back on any anomalies or potential challenges, and the fourth member began breaking down the analysis questions to determine which particular data would be needed to answer the analysis questions.

```{r eval=FALSE}
library(tidyverse)
library(readxl)
library(here)
library(skimr)
library(janitor)

raw_candy_2015 <- read_excel(
  here("raw_data/boing-boing-candy-2015.xlsx")
)

raw_candy_2016 <- read_excel(
  here("raw_data/boing-boing-candy-2016.xlsx")
)

raw_candy_2017 <- read_excel(
  here("raw_data/boing-boing-candy-2017.xlsx")
)
```


### **2.2. Breakdown of Tasks**

The group reconvened and determined that a significant portion of the data would not be needed to carry out the analysis, therefore we would standardise the individual raw datasets to contain the following columns:

*Combined_ID*    
*Year*    
*Age*  
*Trick or Treat*  
*Candy Type*  
*Rating*  
*Country*  
*State or Province*  
*Gender*  

From this we would use the '(rbind)' function to combine the datasets into one, which could be further tidied and refined.

# **3. Approach**

### **3.1. Individual Datasets - Initial Cleaning**

As a group we collaborated on writing code that could be used to streamline the 2015 data, tested to ensure it worked as expected:

```{r eval=FALSE}
candy_clean_2015 <- clean_names(raw_candy_2015) %>% 
  mutate(Year = as.numeric(str_sub(timestamp, start = 1, end = 4)),
         .before = timestamp,
         Dataset = Year) %>% 
  rowid_to_column("ID") %>%
  rename("Age" = "how_old_are_you", 
         "Trick_or_Treat" = "are_you_going_actually_going_trick_or_treating_yourself") %>% 
  unite("Combined_ID", c("Dataset", "ID"), sep = "_") %>% 
  pivot_longer(cols = c("butterfinger":"york_peppermint_patties"),
               names_to = "Candy_Type",
               values_to = "Rating") %>% 
  add_column(Country = NA,
             State_or_Province = NA,
             Gender = NA) %>% 
  select("Combined_ID", "Year", "Age", "Trick_or_Treat", "Candy_Type", "Rating", "Country", "State_or_Province", 
         "Gender"); 
```

Once we were confident that this code functioned as intended, we applied it to the datasets for 2016 and 2017 customising the code to account for differences in the raw data compared to the 2015 dataset: 

```{r eval=FALSE}
candy_clean_2016 <- clean_names(raw_candy_2016) %>% 
  mutate(Year = as.numeric(str_sub(timestamp, start = 1, end = 4)),
         .before = timestamp,
         Dataset = Year) %>% 
  rowid_to_column("ID") %>%
  rename("Age" = "how_old_are_you",
         "Trick_or_Treat" = "are_you_going_actually_going_trick_or_treating_yourself",
         "Gender" = "your_gender",
         "Country" = "which_country_do_you_live_in",
         "State_or_Province" = "which_state_province_county_do_you_live_in") %>% 
  unite("Combined_ID", c("Dataset", "ID"), sep = "_") %>% 
  pivot_longer(cols = c("x100_grand_bar":"york_peppermint_patties"),
               names_to = "Candy_Type",
               values_to = "Rating") %>%
  select("Combined_ID", "Year", "Age", "Trick_or_Treat", "Candy_Type", "Rating", "Country", "State_or_Province", 
         "Gender");

candy_clean_2017 <- clean_names(raw_candy_2017) %>% 
  rename("Age" = "q3_age", 
         "Gender" = "q2_gender", 
         "Trick_or_Treat" = "q1_going_out", 
         "Country" = "q4_country", 
         "State_or_Province" = "q5_state_province_county_etc") %>%
  rowid_to_column("ID") %>%
  add_column(Year = "2017") %>%
  mutate(Dataset = Year) %>% 
  unite("Combined_ID", c("Dataset", "ID"), sep = "_") %>% 
  pivot_longer(cols = ("q6_100_grand_bar":"q6_york_peppermint_patties"),
               names_to = "Candy_Type",
               values_to = "Rating") %>% 
  
  select("Combined_ID", "Year", "Age", "Trick_or_Treat", "Candy_Type", "Rating", "Country", "State_or_Province", 
         "Gender")
```

These datasets were then combined together using the (rbind) function to make one dataset, and futher refinement and cleaning made to prepare it for analysis.

```{r eval=FALSE}

merged_candy_data_171819 <-rbind(candy_clean_2015, candy_clean_2016, candy_clean_2017) 

# Tidy the merged dataset

  #Country data - changing to title case
  tidied_candy_data <- merged_candy_data_171819  %>% 
  mutate(Country_clean = str_to_title(Country),
         .after = Country) %>% 
  
  #cleaning data for US entries
  mutate(Country_clean = 
           case_when(Country_clean %in% c("'Merica",
                                        "Ahem....Amerca",
                                        "Alaska",
                                        "America",
                                        "California",
                                        "Eua",
                                        "I Pretend To Be From Canada, But I Am Really From The United States.",
                                        "Merica",
                                        "Murrika",
                                        "N. America",
                                        "Narnia",
                                        "New Jersey",
                                        "New York",
                                        "North Carolina",
                                        "Pittsburgh",
                                        "The Best One - Usa",
                                        "The United States Of America",
                                        "The United States",
                                        "The Yoo Ess Of Aaayyyyyy",
                                        "Trumpistan",
                                        "U S A",
                                        "U S",
                                        "U.s.",
                                        "U.s.a.",
                                        "Ud",
                                        "Unhinged States",
                                        "Unied States",
                                        "Unite States",
                                        "United  States Of America",
                                        "United Sates",
                                        "United Staes",
                                        "United State",
                                        "United Statea",
                                        "United Stated",
                                        "united states",
                                        "United States Of America",
                                        "United States",
                                        "United Statss",
                                        "United Stetes",
                                        "United Ststes",
                                        "Unites States",
                                        "Units States",
                                        "Us Of A",
                                        "Us",
                                        "Usa (I Think But It's An Election Year So Who Can Really Tell)",
                                        "Usa Usa Usa Usa",
                                        "Usa Usa Usa!!!!",
                                        "Usa Usa Usa",
                                        "Usa! Usa! Usa!", 
                                        "Usa! Usa!", 
                                        "Usa!!!!!!",
                                        "Usa!",
                                        "Usa",
                                        "uSA",
                                        "usa",
                                        "Usa? Hard To Tell Anymore..",
                                        "Usaa",
                                        "Usas",
                                        "Usausausa",
                                        "USSA",
                                        "Ussa",
                                        "united states") ~ "US",
                     (Country_clean == "Cascadia") & (State_or_Province == "WA") ~ "US",
                     (Country_clean == "Murica") & (State_or_Province == "Oregon") ~ "US",
                     (Country_clean == "Murica") & (State_or_Province == "California") ~ "US",
                     (Country_clean == "Murica") & (State_or_Province == "NJ") ~ "US",
                     (is.na(Country_clean)) & (State_or_Province == "CA") ~ "US",
                     (is.na(Country_clean)) & (State_or_Province == "WA") ~ "US",
                     (is.na(Country_clean)) & (State_or_Province == "PA") ~ "US",
                     (is.na(Country_clean)) & (State_or_Province == "Massachusetts") ~ "US",
                     (is.na(Country_clean)) & (State_or_Province == "Arizona") ~ "US",
                     (is.na(Country_clean)) & (State_or_Province == "Illinois") ~ "US",
                     (is.na(Country_clean)) & (State_or_Province == "United States") ~ "US",
                     (is.na(Country_clean)) & (State_or_Province == "USA") ~ "US",
                     
                     #cleaning data for UK entries                     
                     Country_clean %in% c("United Kindom",
                                        "England",
                                        "Endland",
                                        "Scotland",
                                        "U.k.",
                                        "Uk",
                                        "United Kingdom") ~ "UK",
                     
                     #cleaning data for Canada entries  
                     Country_clean %in% c("Can",
                                        "Canada`",
                                        "Canae") ~ "Canada",
                     
                     #general cleaning
                     Country_clean == "Netherlands" ~ "The Netherlands",
                     Country_clean == "Uae" ~ "UAE",
                     Country_clean == "Brasil" ~ "Brazil",
                     Country_clean == "España" ~ "Spain",
                     (Country_clean == "Korea") & (State_or_Province == "Incheon") ~ "South Korea",
                     
                     #Where Country column contains a number but State/ Province indicates the country is the US
                     Country_clean == "32" ~ "US",
                     Country_clean == "45" ~ "US",
                     Country_clean == "46" ~ "US",
                     Country_clean == "35" ~ "US",
                     Country_clean == "30.0" ~ "US",
                     Country_clean == "45.0" ~ "US",
                     Country_clean == "44.0" ~ "US",
                     Country_clean == "54.0" ~ "US",
                     Country_clean == "47.0" ~ "US",
                     Country_clean == "51.0" ~ "US",
                     
                     #cleaning data for Unknown Country entries 
                     Country_clean %in% c("1",
                                        "A",
                                        "A Tropical Island South Of The Equator",
                                        "Atlantis",
                                        "Earth",
                                        "Europe",
                                        "Fear And Loathing",
                                        "God's Country",
                                        "Insanity Lately",
                                        "I Don't Know Anymore",
                                        "Neverland",
                                        "Not The Usa Or Canada",
                                        "One Of The Best Ones",
                                        "See Above",
                                        "Somewhere",
                                        "Soviet Canuckistan",
                                        "Subscribe To Dm4uz3 On Youtube",
                                        "Sub-Canadian North America... 'Merica",
                                        "The Republic Of Cascadia",
                                        "There Isn't One For Old Men",
                                        "This One",
                                        "Denial") ~ "Unknown Country",
                     (Country_clean == "Cascadia") & (State_or_Province == "cascadia") ~ "Unknown Country",
                     (is.na(Country_clean)) & (is.na(State_or_Province)) ~ "Unknown Country",
                     (is.na(Country_clean)) & (State_or_Province == "48") ~ "Unknown Country",
                     (Country_clean == "Murica") & (State_or_Province == "Gawja") ~ "Unknown Country",
                     TRUE ~ Country_clean
           )
  ) %>% 
  
  
  #cleaning data for candy type 
  
    mutate(Candy_clean = str_replace_all(Candy_Type,"^q6_","")) %>% 
    mutate(Candy_clean = str_replace_all(Candy_clean, "_", " ")) %>% 
    mutate(Candy_clean =
                       # Invalid responses
                       case_when(Candy_clean %in% c(
                         "abstained from m ming",
                         "bonkers the board game",
                         "box o raisins",
                         "boxo raisins",
                         "broken glow stick",
                         "candy that is clearly just the stuff given out for free at restaurants",
                         "cash or other forms of legal tender",
                         "chardonnay",
                         "creepy religious comics chick tracts",
                         "dental paraphenalia",
                         "generic brand acetaminophen",
                         "healthy fruit",
                         "hugs actual physical hugs",
                         "joy joy mit iodine",
                         "kale smoothie",
                         "lapel pins",
                         "minibags of chips",
                         "person of interest season 3 dvd box set not including disc 4 with hilarious outtakes",
                         "peterson brand sidewalk chalk",
                         "real housewives of orange county season 9 blue ray",
                         "spotted dick",
                         "vials of pure high fructose corn syrup for main lining into your vein",
                         "vicodin",
                         "whatchamacallit bars",
                         "white bread",
                         "whole wheat anything") ~ "invalid_response",
                         
                         # Rename 
                         Candy_clean == "anonymous brown globs that come in black and orange wrappers" ~ "mary janes",
                         Candy_clean == "anonymous brown globs that come in black and orange wrappers a k a mary janes" ~ "mary janes",
                         Candy_clean == "chick o sticks we don t know what that is" ~ "chick o stick",
                         Candy_clean == "gummy bears straight up" ~ "gummy bears",
                         Candy_clean == "licorice yes black" ~ "black licorice",
                         Candy_clean == "nown laters" ~ "now and later",
                         Candy_clean == "sandwich sized bags filled with boo berry crunch" ~ "boo berry crunch",
                         Candy_clean == "sourpatch kids i e abominations of nature" ~ "sourpatch kids",
                         Candy_clean == "sweetums a friend to diabetes" ~ "sweetums",
                         Candy_clean == "those odd marshmallow circus peanut things" ~ "marshmallow circus peanuts",
                         Candy_clean == "tolberone something or other" ~ "toblerone",
                         Candy_clean == "x100 grand bar" ~ "100 grand bar",
                         TRUE ~ Candy_clean)
              ) %>% 
  
  #cleaning data for age
    mutate(Age_clean = str_replace_all(Age, "\\.0$","")) %>% 
    
    #cleaning data for age unknown
    mutate(Age_clean = 
             case_when(Age_clean %in% c("your mom",
                                        "x",
                                        "very",
                                        "Too old to trick or treat without it being creepy",
                                        "too old for this",
                                        "Too old",
                                        "too old",
                                        "too",
                                        "So old",
                                        "See question 2",
                                        "Same as yo mama",
                                        "really old",
                                        "over retirement age",
                                        "Over 50",
                                        "over 40",
                                        "Older than you",
                                        "older than I want to be",
                                        "Older than i act",
                                        "older than dirt",
                                        "Old, very old",
                                        "old enough to party",
                                        "Old enough to not Trick or Treat.",
                                        "Old enough to know better",
                                        "old enough to know better",
                                        "Old enough",
                                        "old enough",
                                        "old but still know joy from despair",
                                        "OLD",
                                        "Old",
                                        "old",
                                        "Not tell",
                                        "Not as old as you...",
                                        "none of your business",
                                        "no",
                                        "Nevermind",
                                        "Never ask a woman that question.",
                                        "MY NAME JEFF",
                                        "middle-aged",
                                        "Many",
                                        "In dog years?",
                                        "I remember the Nixon administration",
                                        "I can remember when Java was a cool new language",
                                        "Hahahahahaha",
                                        "hahahahaha",
                                        "gofuckyourself",
                                        "Enough",
                                        "enough",
                                        "dadt",
                                        "blah",
                                        "As old as my tongue a few years older than my teeth",
                                        "Ancient",
                                        "ancient",
                                        "Adult",
                                        "--",
                                        "45-55",
                                        "50+",
                                        "55+",
                                        "60+",
                                        "65+",
                                        ">39",
                                        "?",
                                        "７１＋",
                                        "0x2A",
                                        "24-50",
                                        "30's",
                                        "30s",
                                        "30+",
                                        "40s",
                                        "50ish",
                                        "40something",
                                        "5 months",
                                        "1.0E18",
                                        "9.0E22",
                                        "0.62",
                                        "a million") ~ "unknown age",
                       (is.na(Age_clean))~ "unknown age",
                       
    #general cleaning
                       Age_clean == "sixty-nine" ~ "69",
                       Age_clean == "Good Lord!  I'm 43!" ~ "43",
                       Age_clean == "Fifty.  Nine.  Ish." ~ "59",
                       Age_clean == "27^." ~ "27",
                       Age_clean == "37 (I'm taking a child)" ~ "37",
                       Age_clean == "40. Deal with it." ~ "40",
                       Age_clean == "42 - I'm taking my kid" ~ "42",
                       Age_clean == "46 Halloweens." ~ "46",
                       Age_clean == "49 11/12ths" ~ "49",
                       Age_clean == "50 (despair)" ~ "50",
                       Age_clean == "50, taking a 13 year old." ~ "50",
                       Age_clean == "70.5" ~ "70",
                       Age_clean == "44.4444" ~ "44",
                       Age_clean == "39.4" ~ "39",
                       Age_clean == "23.2" ~ "23",
                       Age_clean == "18.75" ~ "18",
                       Age_clean == "18.17" ~ "18",
                       Age_clean == "45, but the 8-year-old Huntress and bediapered Unicorn give me political cover and social respectability.  However, I WILL eat more than they do combined." ~ "45",
                       Age_clean == "59 on the day after Halloween" ~ "58",
                       Age_clean == "27^" ~ "27",
                       TRUE ~ Age_clean
             )
    ) %>% 
    
    mutate(Age_clean = str_replace_all(Age_clean, "[:punct:]$","")) %>% 
    mutate(Age_clean = str_replace_all(Age_clean, "^$","")) %>% 
    mutate(Age_clean = str_replace_all(Age_clean, "[s-z]$","")) %>% 
    mutate(Age_clean = as.numeric(Age_clean))
  
final_candy_data <- tidied_candy_data %>% 
  select(-"Age", -"Candy_Type", -"Country") %>% 
  rename("Age" = "Age_clean", "Candy_Type" = "Candy_clean", "Country" = "Country_clean")

```



### **3.2. General Assumptions**

**Age assumptions**
- Observations that did not contain an age value were removed
- Observations that contained valid ages with the age spelled in characters were converted to digits
- Observations where a definitive age could not be determined were removed, for example '24-50'/'50ish'
- Observations written in scientific notation were removed
- Observations with a decimal point were converted to whole numbers

**Country assumptions**
- Code was created to convert known variations of country names to the appropriate match, i.e. 'USA', 'United States', 'US', 'America' etc. to show as "US"
- Where no country was reported, but the respondent had reported a state or province, this was matched
to show the corresponding country using our best estimations.
- Unclear/ambiguous entries were converted to "Invalid Response", i.e. 'Somewhere'/ 'Not the USA or Canada'


# **4. Analysis and Observations**


**Q1.  What is the total number of candy ratings given across the three years.**
**(Number of candy ratings, not the number of raters. Don’t count missing values)**

*OBSERVATION - A filter was applied to the 'Rating' column, to exclude responses with no ratings*

```{r eval=FALSE}
final_candy_data %>% 
  filter(Rating %in% c("DESPAIR","MEH","JOY")) %>% 
  nrow();
```


**Q2.  What was the average age of people who are going out trick or treating?**

*OBSERVATION - For questions 2 and 3 a unique ID column 'Combined_id' was created at the initial cleaning stage of the individual raw datasets, in order to capture the number of unique respondents. Additionally, a filter was applied to the 'Age' column data to ensure only ages under 100 were used in the analysis.*

```{r eval=FALSE}
final_candy_data %>% 
  select(Age, Trick_or_Treat, Combined_ID) %>% 
  distinct(Age, Trick_or_Treat, Combined_ID) %>% 
  filter(Age <= 100) %>% 
  filter(Trick_or_Treat == "Yes") %>% 
  summarise(average_age_trick_or_treat = round(mean(Age, na.rm = TRUE))); 
```


**Q3. What was the average age of people who are not going trick or treating?** 


```{r eval=FALSE}
final_candy_data %>% 
  select(Age, Trick_or_Treat, Combined_ID) %>% 
  distinct(Age, Trick_or_Treat, Combined_ID) %>% 
  filter(Age <= 100) %>% 
  filter(Trick_or_Treat == "No") %>% 
  summarise(average_age_not_trick_or_treat = round(mean(Age, na.rm = TRUE))); 
```
         
         
**Q4.  For each of joy, despair and meh, which candy bar received the most of these ratings?**
        
*OBSERVATION - The response 'any full sized candy bar' received most of the 'JOY' ratings; however for the purposes of obtaining more accurate analysis the group decided to filter that response out.*
         
```{r eval=FALSE}
final_candy_data %>% 
  filter(Candy_Type != "invalid_response") %>% 
  filter(Rating %in% c("JOY", "DESPAIR", "MEH")) %>% 
  filter(Candy_Type != "any full sized candy bar") %>% 
  count(Rating, Candy_Type) %>% 
  group_by(Rating) %>% 
  slice(which.max(n));
```
         
         
**Q5.  How many people rated Starburst as despair?**
         
```{r eval=FALSE}
final_candy_data %>% 
  select(Candy_Type, Rating) %>% 
  filter(Rating == "DESPAIR") %>% 
  filter(Candy_Type == "starburst") %>% 
  count(Rating, Candy_Type);
```
         
  
**For the next three questions, count despair as -1, joy as +1, and meh as 0.** 

*OBSERVATION - A new dataframe was created to assign the numeric weightings to the ratings, for use in questions 7-9.*
         
```{r eval=FALSE}
candy_ratings_with_values <- final_candy_data %>% 
  mutate(numeric_rating = case_when(
    Rating == "DESPAIR" ~ "-1",
    Rating == "JOY" ~ "1",
    Rating == "MEH" ~ "0")) %>% 
      mutate(numeric_rating = as.numeric(numeric_rating));
```
         
         
**Q6.  What was the most popular candy bar by this rating system for each gender in the dataset?** 
         
*OBSERVATION - "any full sized candy bar" is the most popular for each gender therefore decided to filter this out to get more meaningful data*
        
```{r eval=FALSE} 
candy_ratings_with_values %>% 
  select(Candy_Type, numeric_rating, Gender) %>% 
  group_by(Gender, Candy_Type) %>% 
  summarise(rating_count = sum(numeric_rating, na.rm = TRUE)) %>% 
  filter(Candy_Type != "any full sized candy bar") %>% 
  filter(rating_count == max(rating_count)) %>% 
  arrange(Gender, Candy_Type, rating_count);
```
         
         
**Q7.  What was the most popular candy bar in each year?** 

*OBSERVATION - "any full sized candy bar" is the most popular in each year therefore decided to filter this out to get more meaningful data*
         
```{r eval=FALSE}
         candy_ratings_with_values %>% 
           select(Candy_Type, numeric_rating, Year) %>% 
           group_by(Year, Candy_Type) %>% 
           summarise(rating_count = sum(numeric_rating, na.rm = TRUE)) %>% 
           filter(Candy_Type != "any full sized candy bar") %>% 
           filter(rating_count == max(rating_count)) %>% 
           arrange(Year, Candy_Type, rating_count);
```


**Q8.  What was the most popular candy bar by this rating for people in US, Canada, UK, and all other countries?** 

```{r eval=FALSE}
# Canada and UK
candy_ratings_with_values %>% 
  select(Candy_Type, numeric_rating, Country) %>% 
  filter(Country %in% c("US", "Canada", "UK")) %>%
  group_by(Country, Candy_Type) %>% 
  summarise(Rating_Count = sum(numeric_rating, na.rm = TRUE)) %>% 
  filter(Candy_Type != "any full sized candy bar") %>% 
  filter(Rating_Count == max(Rating_Count)) %>% 
  arrange(-Rating_Count);

# All other countries
candy_ratings_with_values %>% 
  select(Candy_Type, numeric_rating, Country) %>% 
  filter(Country != c("US", "Canada", "UK")) %>%
  group_by(Candy_Type) %>% 
  summarise(Rating_Count_Other_Countries = sum(numeric_rating, na.rm = TRUE)) %>% 
  filter(Candy_Type != "any full sized candy bar") %>% 
  filter(Rating_Count_Other_Countries == max(Rating_Count_Other_Countries))
```
# **5. Visualisations**

```{r eval=FALSE}
# Tidy Canada Provinces   

canada_provinces <- final_candy_data %>% 
  filter(Country == "Canada") %>% 
   mutate(State_or_Province =
      case_when(State_or_Province %in% c("AB","Albeqrrta", "alberta") ~ "Alberta",
          State_or_Province %in% c("BC", "Bc", 
                                         "bc", "british columbia", 
                                         "vancouver, bc", 
                                         "British Columbia, Canada") ~ "British Columbia",
          State_or_Province == "NB" ~ "New Brunswick",
          State_or_Province %in% c("Newfoundland", "St. John's, NL", 
                                         "NL", "newfoundland") ~ "Newfoundland and Labrador",
          State_or_Province %in% c("nova scotia", "ns", "NS") ~ "Nova Scotia",
          State_or_Province %in% c("ON", "ontario", "Oshawa, Ontario, 
                                         Canada", "Ont", "Ontario,  Canada", 
                                         "Toronto, Ontario", "On", "ont", 
                                         "ONTARIO", "Oshawa, Ontario, Canada") ~ "Ontario",
          State_or_Province %in% c("Quebec, Canada", "QC", "Québec", 
                                         "Quenec", "quebec", "québec") ~ "Quebec",
          State_or_Province %in% c("ON", "ontario", "Ont", "Ontario, 
                                         Canada") ~ "Ontario",
          State_or_Province == "yukon" ~ "Yukon",
          State_or_Province == "manitoba" ~ "Manitoba",
          State_or_Province == "sk" ~ "Saskatchewan",
          TRUE ~ State_or_Province)
      );
```
   
   
```{r eval=FALSE}
number_of_candy_ratings_per_Province <- canada_provinces %>% 
  filter(Rating %in% c("JOY", "MEH", "DESPAIR")) %>% 
  filter(State_or_Province %in% c(
    "Alberta",
    "British Columbia",
    "Manitoba",
    "New Brunswick",
    "Newfoundland and Labrador",
    "Nova Scotia",
    "Ontario",
    "Prince Edward Island",
    "Quebec",
    "Saskatchewan",
    "Yukon")) %>% 
  select(State_or_Province) %>% 
  count(State_or_Province) %>% 
  group_by(State_or_Province) 
```
   
   
```{r eval=FALSE}
ggplot(
  number_of_candy_ratings_per_Province, 
  aes(x = State_or_Province, y = n, fill = State_or_Province)) +
  geom_col(show.legend = FALSE) +
  labs(
    x = "Province",
    y = "Number of ratings",
    title = "Total number of Candy Ratings split by Canadian Province",
    subtitle = "data from 2015-2017 incl 'Joy', 'Meh' and 'Despair' ratings") +
  coord_flip() 
``` 
```













    